\section{Work Packages and Timeline}

This project is divided into six distinct work packages. The first one is for gaining the necessary theoretical background for understanding the measurement-based computing model. This first phase involves literature search and reading on \emph{graph states}, which are essential to building a working knowledge of \emph{cluster states.} The second working package is about taking this theoretical framework and applying it to the model. With this phase, we plan to build a solid understanding of how measurement-based computation works and learn some applications of this computing schema. With the third package, we use the technical knowledge built by the previous two packages to write the introduction and method parts of the final report. The fourth working package involves literature research seeking suitable algorithm candidates to re-formulate using a measurement-based model. After selecting the algorithm, we will re-formulate the problem as mentioned and conduct some resource requirement/performance analysis. The last two packages are for the preparation of our poster and the finalization of our final report.

The timeline and succinct descriptions of working packages are given in Table \ref{tab:wp}.

\begin{table}[htb]
  \center
  \newcommand\cc{\blacksquare}
  \subcaptionbox{Project Timeline\label{tab:wp:timeline}}{%
    \begin{tabular}{r @{\hspace{2em}}c c c c c c c c c c c c c c}
      \toprule
        & \multicolumn{13}{c}{Week} \\\cmidrule{2-14}
      WP &  2 &  3 &  4 &  5 &  6 &  7 &  8 &  9 & 10 & 11 & 12 & 13 & 14 \\
      \midrule
      1 & \cc & \cc & \cc & \cc                                                       \\
      2 &     &     &     & \cc & \cc & \cc & \cc                                     \\
      3 &     &     &     &     & \cc & \cc & \cc                                     \\
      4 &     &     &     &     &     &     &     & \cc & \cc & \cc & \cc & \cc       \\
      5 &     &     &     &     &     &     &     &     &     &     &     & \cc & \cc \\
      6 &     &     &     &     &     &     &     &     &     &     & \cc & \cc & \cc \\
      \bottomrule
    \end{tabular}}\vspace{\baselineskip}

  \subcaptionbox{Description of Work Packages\label{tab:wp:description}}{
    \begin{tabular}{r@{\hspace{2em}}p{0.8\linewidth}}
      \toprule
      WP & Description \\
      \midrule
      \renewcommand*{\arraystretch}{1.5}
      1 & Literature search and reading on theoretical background, including \emph{graph states} and \emph{cluster states.} \\
      2 & Thorough literature review on measurement-based quantum computing.\\
      3 & Writing of the introduction and methods parts of the written report.\\
      4 & Application of a suitable and well-known quantum algorithm to a measurement-based computing model.\\
      5 & Preparation of the poster.\\
      6 & Finalization of the written report.\\
      \bottomrule
    \end{tabular}}
    \caption{General timeline of the project and work package descriptions\label{tab:wp}}
\end{table}

